### 2017-09-09 paper/evaluation.tex
pass on RQ5

To answer \numRQSpeedupOne{}, we considered the \numProjectsPar{}
subjects from our benchmark that use parallelization \emph{by default}
(see Table~\ref{tab:freqmodes-dynamic}).  We compared running times
with parallelization~---~configured by project owners and without
parallelization.

@@

Table~\ref{tab:speedup} summarizes results.
Lines are sorted by project names.
Columns ``\emph{Group}'' and ``\emph{Name}'' indicate, respectively,
the group and the name of the subject.
Column ``$T_s$'' shows sequential execution time and column ``$T_p$''
shows parallel execution time.
Column ``$T_s/T_p$'' shows speedup or slowdown.
As usual, a ratio above 1x indicates speedup and a ratio below 1x
indicates slowdown.

Results show that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.
Three cases worth special attention: \CodeIn{Log4J2}, \CodeIn{Chaos},
and \CodeIn{Takes}.
We note that parallel execution in \CodeIn{Log4J2} was
ineffective.  We found that Maven invokes several test modules in this
project but the test modules that dominate execution time run
sequentially by default. This was also the case of the highlighted
project \CodeIn{Californium}.
No significant speedup was observed in \CodeIn{Chaos}, a project with
only three test classes, of which one monopolizes the bulk of test
execution time.

\begin{table}[ht!]
\centering
\resizebox{.41\textwidth}{!}{%
  \scriptsize
\begin{tabular}{llrrr}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & Californium & 1.45m & 1.40m & \cellcolor{lightgray}1.04x\\%
Medium & \Comment{BounceStorage} Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & \cellcolor{lightgray}1.03x\\%
Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
Medium &Javaslang& 2.18m & 1.82m & 1.20x\\%
Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m & 9.20x\\%
Long &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
Long & \Comment{apache} Mahout & 27.38m & 18.15m & 1.51x\\%
Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
Medium & \Comment{apache} OpenNLP & 1.30m & 0.55m & 2.36x\\%
Medium & \Comment{yegor256} Rultor & 2.30m & 0.27m & 8.52x\\%
Medium & \Comment{yegor256} Takes & 2.00m & 0.19m & \cellcolor{lightgray}10.53x\\%
Long & \Comment{vavr-io} Vavr & 3.26m & 2.25m & 1.45x\\%
\midrule
\textbf{average} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\vspace{-5ex}
\end{tabular}}
\caption{\label{tab:speedup}Speedup (or slowdown) of parallel
  execution ($T_p$) over sequential execution ($T_s$).  Default
  parallel configuration of Maven is used.  Highest slowdown/speedup
  appears in gray color.}
\end{table}
This project uses configuration \ParClassSeqMeth{}, which runs test
classes in parallel but runs test methods, declared in each class,
sequentially.
Consequently, speedup cannot be obtained as the cost of the single
expensive test class cannot be broken down with the selected
configuration.
Finally, the speedup observed in project \CodeIn{Takes} was
the highest amongst all projects. This subject uses configuration
\ParClassParMeth{} and contains 419 test methods distributed nearly
equally among 148 test classes with a small number of test methods.
Furthermore, several methods in those classes are time-consuming.
As result, the CPUs available for testing are kept occupied for the
most part during test execution.

>>>>

@@

To answer \numRQSpeedupOne{}, we considered the \numProjectsPar{}
subjects from our benchmark that use parallelization \emph{by default}
(see Table~\ref{tab:freqmodes-dynamic}).  We compared running times
of test suites with enabled parallelization, as configured by project
developers, and without parallelization.
Table~\ref{tab:speedup} summarizes results.
Lines are sorted by project names.
Columns ``\emph{Group}'' and ``\emph{Subject}'' indicate, respectively,
the cost group and the name of the project.
Column ``$T_s$'' shows sequential execution time and column ``$T_p$''
shows parallel execution time.
Column ``$T_s/T_p$'' shows speedup or slowdown.
As usual, a ratio above 1x indicates speedup and a ratio below 1x
indicates slowdown.

\begin{table}[t!]
\centering
\resizebox{.41\textwidth}{!}{%
  \scriptsize
\begin{tabular}{llrrr}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & Californium & 1.45m & 1.40m & \cellcolor{lightgray}1.04x\\%
Medium & \Comment{BounceStorage} Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & \cellcolor{lightgray}1.03x\\%
Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
Medium &Javaslang& 2.18m & 1.82m & 1.20x\\%
Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m & 9.20x\\%
Long &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
Long & \Comment{apache} Mahout & 27.38m & 18.15m & 1.51x\\%
Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
Medium & \Comment{apache} OpenNLP & 1.30m & 0.55m & 2.36x\\%
Medium & \Comment{yegor256} Rultor & 2.30m & 0.27m & 8.52x\\%
Medium & \Comment{yegor256} Takes & 2.00m & 0.19m & \cellcolor{lightgray}10.53x\\%
Long & \Comment{vavr-io} Vavr & 3.26m & 2.25m & 1.45x\\%
\midrule
\textbf{average} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\vspace{-5ex}
\end{tabular}}
\caption{\label{tab:speedup}Speedup (or slowdown) of parallel
  execution ($T_p$) over sequential execution ($T_s$).  Default
  parallel configuration of Maven is used.  Highest slowdown/speedup
  appears in gray color.}
\end{table}

Results show that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.
Three cases worth special attention: \CodeIn{Log4J2}, \CodeIn{Chaos},
and \CodeIn{Takes}.
We note that parallel execution in \CodeIn{Log4J2} was
ineffective.  We found that Maven invokes several test modules in this
project but the test modules that dominate execution time run
sequentially by default. This was also the case for the highlighted
project \CodeIn{Californium}.
No significant speedup was observed in \CodeIn{Chaos}, a project with
only three test classes, of which one monopolizes the bulk of test
execution time.
This project uses configuration \ParClassSeqMeth{}, which runs test
classes in parallel but runs test methods, declared in each class,
sequentially.
Consequently, speedup cannot be obtained as the cost of the single
expensive test class cannot be broken down with the selected
configuration.
Finally, the speedup observed in project \CodeIn{Takes} was
the highest amongst all projects. This subject uses configuration
\ParClassParMeth{} and contains 419 test methods distributed nearly
equally among 148 test classes with a small number of test methods.
Furthermore, several methods in those classes are time-consuming.
As result, the CPUs available for testing are kept occupied for the
most part during test execution.
